### 2023-01-31 manuscript.tex
Merge branch 'main' of github.com:stain/2022-fdo-paper into main [ci skip]
This build is based on
https://github.com/stain/2022-fdo-paper/commit/c0dc59e999a0bc215e5d5e0509a2cf6927bcbba4.

This commit was created by the following CI build and job:
https://github.com/stain/2022-fdo-paper/commit/c0dc59e999a0bc215e5d5e0509a2cf6927bcbba4/checks
https://github.com/stain/2022-fdo-paper/actions/runs/4055104070

This manuscript
(\href{https://stain.github.io/2022-fdo-paper/v/a78fcc264323c8aac5b5620d946ef6d07686c498/}{permalink})
was automatically generated
from \href{https://github.com/stain/2022-fdo-paper/tree/a78fcc264323c8aac5b5620d946ef6d07686c498}{stain/2022-fdo-paper@a78fcc2}
on January 31, 2023.

>>>>

This manuscript
(\href{https://stain.github.io/2022-fdo-paper/v/c0dc59e999a0bc215e5d5e0509a2cf6927bcbba4/}{permalink})
was automatically generated
from \href{https://github.com/stain/2022-fdo-paper/tree/c0dc59e999a0bc215e5d5e0509a2cf6927bcbba4}{stain/2022-fdo-paper@c0dc59e}
on January 31, 2023.
